Renewal and stability in populations structured by remaining years of life

### 2014-09-02 ThanoRepro/ThanoRepro.tex
starting proof appendix
mostly finished appendix B, included pressat in bib

\documentclass{article}
\usepackage{amsmath}
\usepackage{caption}
\usepackage{placeins}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{tikz}
%\usepackage[active,tightpage]{preview}
\usepackage{natbib}
\bibpunct{(}{)}{,}{a}{}{;} 
\usepackage{url}
\usepackage{nth}
% for the d in integrals
\newcommand{\dd}{\; \mathrm{d}}

@@

* this is a work in progress, and by the time the EPC comes around I'll
have shifted the focus away on comparing stable results estimated from data
(the last couple figures), and more toward the reversibility of chronological
and thanatological stable age structures, as well as a comparative
eigen-analysis of the Leslie and thanatological projection matrices.

@@

\appendix
\section{Unique solution for thanatological $r$}
\label{app:A}
The solution for the intrinsic growth rate, $r$, is unique for the case of the
thanatological renewal model, \eqref{eq:thanoren}, and can be proven so in
essentially the same fashion as those in existence for the Lotka-Euler model,
\eqref{eq:lotka}. This little proof follows that given in
\textit{pressat1972demographic}. Define a convenience function, $I(r)$, for the
integrand of \eqref{eq:thanoren} for a given $r$ and fixed $f^\star(y)$ and $d(a)$:

@@

\nocite{HMD,HFD}
% --------------------------------------------------
% bibliography
\bibliographystyle{plainnat}
  \bibliography{References}

>>>>

\documentclass{article}
\usepackage{appendix}
\usepackage{amsmath}
\usepackage{caption}
\usepackage{placeins}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{tikz}
%\usepackage[active,tightpage]{preview}
\usepackage{natbib}
\bibpunct{(}{)}{,}{a}{}{;} 
\usepackage{url}
\usepackage{nth}
% for the d in integrals
\newcommand{\dd}{\; \mathrm{d}}

@@

@@

\begin{appendices}
\section{Unique solution for thanatological $r$}
\label{app:A}
The solution for the intrinsic growth rate, $r$, is unique for the case of the
thanatological renewal model, \eqref{eq:thanoren}, and can be proven so in
essentially the same fashion as those in existence for the Lotka-Euler model,
\eqref{eq:lotka}. This little proof follows that given in
\citet{pressat1973analyse}. Define a convenience function, $I(r)$, for the
integrand of \eqref{eq:thanoren} for a given $r$ and fixed $f^\star(y)$ and $d(a)$:

@@

\section{Equivalence in stability}
\label{app:B}
This appendix contains a proof that the thanatological renewal equation implies
the same intrinsic growth rate, $r$, as Lotka's chronological renewal model if
the starting population is stable. This is identical to claiming that the right
side of the rewal equation is equal given the same $r$. Since there is a unique
real solution, demonstrated in the previous appendix, then it is sufficient to
show that the two integral equations are equal under these conditions. The basic
relationship is:
\begin{align}
\int _{a=0}^\infty l(a)e^{-ra}f(a) \dd a &= \int _{y=0}^\infty \int
_{a=0}^\infty d(a+y)e^{-ra}f^\star (y) \dd a \dd y
\intertext{when}
f^\star(y) &= \frac{b^\star(y)}{c^\star(y)} \\
b^\star (y) &= \int_{a=0}^\infty b(a) \mu(a+y))\frac{l(a+y)}{l(a)} \dd a \\
c^\star (y) &= \int_{a=0}^\infty c(a) \mu(a+y))\frac{l(a+y)}{l(a)} \dd a
\intertext{Note that:}
c(a) &= \frac{l(a)r^{-ra}}{\int l(a) e^{-ra} \dd a} \\
b(a) &= f(a)c(a)
\end{align}
Replacing $f^\star (y)$ with the full expanded expression and
plugging into the thanatological renewal equation gives:
\begin{align}
=& \int _{y=0}^\infty \int
_{a=0}^\infty d(a+y)e^{-ra} \frac{\frac{\int_{a=0}^\infty
f(a)l(a)e^{-ra}\mu(a+y)\frac{l(a+y)}{l(a)} \dd a}{\int l(a) e^{-ra} \dd
a}}{\frac{\int_{a=0}^\infty l(a)e^{-ra} \mu(a+y)\frac{l(a+y)}{l(a)} \dd a}{\int l(a) e^{-ra} \dd a}} \dd a \dd y
\intertext{The denominator of $c(a)$ cancels out:}
=& \int _{y=0}^\infty \int
_{a=0}^\infty d(a+y)e^{-ra} \frac{
\int_{a=0}^\infty
f(a)l(a)e^{-ra}\mu(a+y)\frac{l(a+y)}{l(a)} \dd a}{
\int_{a=0}^\infty l(a)e^{-ra} \mu(a+y)\frac{l(a+y)}{l(a)} \dd a} \dd a \dd y
\intertext{Some $l(a)$'s also cancel out:}
=& \int _{y=0}^\infty \int
_{a=0}^\infty d(a+y)e^{-ra} \frac{
\int_{a=0}^\infty
f(a)e^{-ra}\mu(a+y)l(a+y) \dd a}{
\int_{a=0}^\infty e^{-ra} \mu(a+y)l(a+y) \dd a} \dd a \dd y
\intertext{Now $d(a+y) = \mu (a+y)l(a+y)$, so we can cancel the inner integral
with the denominator:}
=& \int _{y=0}^\infty 
\int_{a=0}^\infty
f(a)e^{-ra}\mu(a+y)l(a+y) \dd a \dd y
\intertext{Note also that $l(a) = \int _{x=a}^\infty d(x) \dd x$ (present
livings are future deaths), which brings us back to the chronological
formulation:} =& \int_{a=0}^\infty e^{-ra}l(a)f(a)
\dd a
\end{align}
\end{appendices}
\nocite{HMD,HFD}
% --------------------------------------------------
% bibliography
\bibliographystyle{plainnat}
  \bibliography{References}
